Procedural Terrain \\ {\large Final project for class CS6491 Computer Graphics}

### 2015-11-30 Paper/Paper.tex
improved limitiation chapter of the erosion model

\subsection{Limitations}
The major drawback of the described model is that it relies on a grid. Because of this and the way the outflow flux is computed, rivers are much more likely to flow along the x and y-axis. 
This leads to the clearly visible black stripes in Fig. \ref{fig:erosion3}. Maybe a more accurate flow simulation would improve this problem. This task is part of future work.

>>>>

\subsection{Limitations}
The described model is very sensitive to the chose of the parameters. The timescale must be small enough so that no numerically instabilities are created, but this directly leads to a long computation time. Also the constant values in the erosion model are very crucial: if the factors are too high, the terrain is eroded very quickly. This looks very unrealistic. The presented values produce good results in our experiments, but a deeper analysis of the parameters is necessary in a future work.
